%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {B.S. in Applied Physics and Mathematics, Specialization in Computational Physics and Biophysics} % Degree
    {Moscow Institute of Physics and Technology (National Research University) (\href{https://mipt.ru/english/}{MIPT})} % Institution
    {Moscow, Russia} % Location
    {Sep. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Specialization:} Basics of comp. condensed matter physics, Molecular dynamics, Practice of HPC, Machine learning in condensed matter physics, Comp. statistical mechanics, Soft-matter physics, Comp. solid-state physics}
        \item {\textbf{Mathematics:} Real analysis and Calculus, Differential geometry, Harmonic analysis, Complex Analysis, Analytic geometry, Linear algebra, Differential Equations, Computational Mathematics, LPDE.}
        \item {\textbf{Physics:} General Physics (Mechanics, Thermodynamics and Molecular Physics, Electricity and Magnetism, Physical Optics), Theoretical Mechanics, Field Theory, Quantum Mechanics, Solid State Physics.}
        \item {\textbf{Computer Science:}  C/C++, UNIX-based systems and multithreading, Parallel computations via MPI and CUDA.}
		\item {\textbf{GPA 4.97/5 (9.11/10), top 3\% of the class.}}        
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
