%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Conferences \& Summer schools}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
    
%---------------------------------------------------------

\begin{cventries}

  \cventry
    {\textbf{Polyachenko Y. A.}, Kondratyuk N. D., Stegailov V. V. <<Molecular-Dynamical model of crystalline Lysozyme>> // \href{http://www.ihed.ras.ru/elbrus21/program/restore.php?id=154}{Abstracts of the XXXVI International Conference on Interaction of Intense Energy Fluxes with Matter. 2021.}} % Affiliation/role
    {\href{http://www.ihed.ras.ru/elbrus21/}{XXXVI International Conference on Interaction of Intense Energy Fluxes with Matter}} % Organization/group
    {Kabardino-Balkaria, Russia} % Location
    {1--6 Mar. 2021} % Date(s)
    {}
    
%---------------------------------------------------------

  \cventry
    {\textbf{Polyachenko Y. A.}, Kondratyuk N. D., Stegailov V. V. <<Molecular-dynamical model of the crystalline lysozyme>> // \href{https://mipt.ru/science/5top100/education/courseproposal/\%D0\%A4\%D0\%A4\%D0\%9F\%D0\%A4.pdf\#page=499}{Works of the 63$^{\texttt{\tiny rd}}$ National Scientific MIPT Conference. Fundamental and applied physics. 2020. pp. 498. (in Russian)}} % Affiliation/role 
    {63$^{\textbf{\tiny rd}}$ National Scientific MIPT Conference} % Organization/group
    {Moscow, Russia} % Location
    {23--29 Nov. 2020} % Date(s)
    {}
    

%---------------------------------------------------------
  \cventry
    {Student, * Remote due to COVID} % Affiliation/role
    {\href{https://education.wolfram.com/summer/school/}{Wolfram Summer School 2020}} % Organization/group
    {* Boston, USA} % Location
    {Jun. 28 -- Jul. 17 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {\href{https://community.wolfram.com/groups/-/m/t/2029621}{Implemented} solvent-excluded and solvent-accessible surfaces in wolfram language.}      
        \item {Studied the interconnection between the Wolfram Language and the OS, the integration with the C language, creation of packages.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {\textbf{Polyachenko Y. A.}, Fleita D. Iu., Pisarev V. V., Norman G. E. <<Equilibrium – metastable singularity in the Lennard-Jones system>> // \href{http://www.ihed.ras.ru/elbrus20/program/restore.php?id=78}{Abstracts of the XXXV International Conference on Equations of State for Matter. 2020.}} % Affiliation/role
    {\href{http://www.ihed.ras.ru/elbrus20/}{XXXV International Conference on Equations of State for Matter}} % Organization/group
    {Kabardino-Balkaria, Russia} % Location
    {1--6 Mar. 2020} % Date(s)
    {}

%---------------------------------------------------------

  \cventry
    {\textbf{Polyachenko Y. A.}, Fleita D. Iu., Pisarev V. V., Norman G. E. <<Singularity at the point of transition from equilibrium to metastable states of Lennard-Jones vapor and liquid>> // \href{https://mipt.ru/science/5top100/education/courseproposal/\%D0\%A4\%D0\%A4\%D0\%9F\%D0\%A42.pdf\#page=218}{Works of the 62$^{\texttt{\tiny nd}}$ National Scientific MIPT Conference. Fundamental and applied physics. 2019. pp. 216-217. (in Russian)}} % Affiliation/role
    {62$^{\textbf{\tiny nd}}$ National Scientific MIPT Conference, Specialization <<Fundamental bases of multi-scale atomistic simulation and modeling>>} % Organization/group
    {Moscow, Russia} % Location
    {18--23 Nov. 2019} % Date(s)
    {}

%---------------------------------------------------------

  \cventry
    {\textbf{Polyachenko Y. A.}, Fleita D. Iu., Pisarev V. V., Norman G. E. <<Study of Lennard-Jones system near the boiling point via space-time correlators>> // \href{https://ihed.ras.ru/afon19/abstracts/book_of_abstracts.pdf\#page=10}{Proceedings of 16$^{\texttt{\tiny th}}$ Russian Symposium FAMMS-2019 Foundations of Atomistic Multiscale Modeling and Simulation. 2019. p. 10. (in Russian)}} % Affiliation/role 
    {16$^{\textbf{\tiny th}}$ Symposium FAMMS-2019 Foundations of Atomistic Multiscale Modeling and Simulation.} % Organization/group
    {New Athos, Georgia} % Location
    {15--26 Aug. 2019} % Date(s)
    {}
    
%---------------------------------------------------------
  \cventry
    {Intern} % Affiliation/role
    {Internship at the Russian national educational center \href{https://sochisirius.ru/uploads/f/SiriusAnnualReport2019_en.pdf}{Sirius} in the scientific-technological projects program <<Big Challenges>>} % Organization/group
    {Sochi, Russia} % Location
    {30 Jun. -- 26 Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Helped senior-school students master Linux, Bash, Python, and LAMMPS}
        \item {Guided a group of senior school students in conducting research dedicated to studying collective motion in Lennard-Jones systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student} % Affiliation/role
    {\href{https://www.cecam.org/workshop-details/135}{Summer School on Classical MD for Material Science, Nanotechnology and Biophysics}, \href{https://www.sissa.it/}{SISSA}} % Organization/group
    {Trieste, Italy} % Location
    {10--21 Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
%        \item {Studied and practiced basic MD simulation techniques and programming tools.}
        \item {Studied Dimension reduction, Umbrella sampling, Approaches to polymer and protein dynamics.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
    
  \cventry
    {\textbf{Polyachenko Y.A.}, Timofeev A.V. <<Diffusion in the Lennard-Jones system>>. // \href{https://mipt.ru/science/5top100/education/!\%D0\%A4\%D0\%A4\%D0\%9F\%D0\%A4.pdf\#page=169}{Works of the 61$^{\texttt{\tiny st}}$ National Scientific MIPT Conference. Fundamental and applied physics. 2018. pp. 165-167. (in Russian)}} % Affiliation/role
    {61$^{\textbf{\tiny st}}$ National Scientific MIPT Conference, Specialization <<Fundamental bases of multi-scale atomistic simulation and modeling>>} % Organization/group
    {Moscow, Russia} % Location
    {19--25 Nov. 2018} % Date(s)
    {}
    

%---------------------------------------------------------
\end{cventries}
