%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Achievements}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {Participant} % Award
    {16$^{\textbf{th}}$ Russian Symposium FOAMM. \newline \textit{Polyachenko Y. A., Fleita D. Iu., Pisarev V. V., Norman G. E. <<Study of Lennard-Jones system near the boiling point via space-time correlators>> // Works of the 16$^{\textbf{th}}$ Russian Symposium FOAMM. 2019. p. 10.}} % Event
    {New Athos, Georgia} % Location
    {Aug. 2019 \vspace{15pt}} % Date(s)
    
   % \vspace{5pt}
    
%---------------------------------------------------------
  \cvhonor
    {Awardee} % Award
    {National Physics Olympiad for Undergraduates <<I am a professional>>} % Event
    {Moscow, Russia} % Location
    {28 Jan. 2019 \vspace{5pt}} % Date(s)
    
  %  \vspace{5pt}    

%---------------------------------------------------------
    
  \cvhonor
    {Awardee} % Award
    {National Mathematics Olympiad for Undergraduates <<I am a professional>>} % Event
    {Moscow, Russia} % Location
    {27 Jan. 2019 \vspace{5pt}} % Date(s)    
    
   \vspace{5pt}    
    
%---------------------------------------------------------
  \cvhonor
    {2$^{\textbf{nd}}$ place} % Award
    {61$^{\textbf{st}}$ National Scientific MIPT Conference, Specialization <<Fundamental bases of multi-scale atomistic simulation and modeling>> \newline \textit{Polyachenko Y.A., Timofeev A.V. Diffusion in the Lennard-Jones system. // Works of the 61$^{\textbf{st}}$ National Scientific MIPT Conference. Fundamental and applied physics. 2018. pp. 165-167.}} % Event
    {Moscow, Russia} % Location
    {25 Nov. 2018 \vspace{10pt}} % Date(s)
    
    \vspace{5pt}
    
%---------------------------------------------------------
  \cvhonor
    {Top 10 of the course ($\sim$ 1100 people)} % Award
    {Scientific project competition. MD simulation package was created and used to test and improve MKT equations.} % Event
    {MIPT} % Location
    {Jun. 2018 \vspace{15pt}} % Date(s)
    
%    \vspace{5pt}

%---------------------------------------------------------
  \cvhonor
    {29$^{\textbf{th}}$ place} % Award
    {Russian National Physics Olympiad for high school students.} % Event
    {Kazan, Russia} % Location
    {\vspace{5pt} Apr. 2017} % Date(s)
    
	\vspace{5pt}
	
\end{cvhonors}
